%!TEX root = ../thesis.tex
%Adding the above line, with the name of your base .tex file (in this case "thesis.tex") will allow you to compile the whole thesis even when working inside one of the chapter tex files
\chapter{List of Publications}
\label{chapter:publications}


\begin{enumerate}

\item \textbf{Carley, E.~P.}, Long, D.~M., Byrne P. J., Zucca, P., Bloomfield D.~S., McCauley J., \& Gallagher, P.~T.\\
``Quasiperiodic Acceleration of Electrons by a Plasmoid Driven Shock in the Solar Atmosphere'', \\
\emph{Nature Physics}, Volume 9, pp. 811-896 (2013).

\item \textbf{Carley, E.~P.}, MacAteer, R.~T. J., \& Gallagher, P.~T.\\
``Coronal Mass Ejection Masses, Energies, and Force Estimates Using \emph{STEREO}'', \\
\emph{The Astrophysical Journal}, Volume 752, Issue 1, article id. 36, 8 pp. (2012).

\item Zucca, P., \textbf{Carley, E.~P.},  McCauley, J., Gallagher, P. T., Monstein, C., \& MacAteer, R.~T. J.,\\
``Observations of Low Frequency Solar Radio Bursts from the Rosse Solar-Terrestrial Observatory'', \\
\emph{Solar Physics}, Volume 280, Issue 2, pp. 591-602. (2012).

\item Zucca, P., \textbf{Carley, E.~P.}, Bloomfield, S.~D., \& Gallagher, P.~T.\\
``The formation heights of coronal shocks from 2D density and Alfv\'{e}n speed maps'', \\
\emph{Astronomy \& Astrophysics}, in press (2014).

\item Bloomfield, S.~D., \textbf{Carley, E.~P.}, et al.\\
``A Comprehensive Overview of the 2011 June 7 Solar Storm'', \\
\emph{Astronomy \& Astrophysics}, in review.

\item Morosan, D.~E., Zucca, P., Fallows, R., \textbf{Carley, E.~P.}, \& Gallagher, P.~T.
``The Non-flaring Sun at Low Frequencies with LOFAR", \\
\emph{Astronomy \& Astrophysics}, in review.

\item Bisi, M.~M., Hardwick, S.~A., Fallows, R.~A., Davies, J.~A., Harrison, R.~A., Jensen, E.~A., Morgan, H.,
Wu, C.~C., Asgekar, A.,  Xiong, M.,  {\bf Carley, E. P.} \\
``The first coronal mass ejection observed with the Low Frequency Array (LOFAR)'', \\
\emph{The Astrophysical Journal Supplements}, in review.

\item Pierantoni, G., {\bf Carley, E. P.}, Byrne P. J., \& P\'{e}rez-Su\'{a}rez, D. \\
``A workflow oriented approach to propagation models in heliophysics'', \\
\emph{Computer Science}, in review.

\end{enumerate}

